The complex network of trophic interactions in a subAntarctic oceanic Marine Protected Area

### 2023-05-08 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
2nd version w/ coauthors suggs

We found different relationships between the species trophic level (TL) and the rest of the analysed species-level properties (Figure 4A-D). The most evident significant relationship was with trophic similarity, i.e. the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C). Here it is noteworthy to highlight those high-trophic level species (TL > 3.1) with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Phalacrocorax atriceps* and *Eudyptes chrysocome* (seabirds), and *Lagenorhynchus cruciger* (marine mammals) (Table S3).

@@

We are indebted to all those experts of the working group 'Banco Burdwood' who humbly provided their knowledge to enhance the quality of the present research. It is worth to mention the following researchers: Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba, Argentina), Mariano I. Martinez (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina), Sofía L. Callá (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina),...
Special thanks to G.A. Lovrich the Scientific Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA N-BB Administrators.
This study was funded by Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina. This work is contribution no. XX of the MPA Namuncurá (Law 26.875).

>>>>

We found different relationships between the species trophic level (TL) and the rest of the analysed species-level properties (Figure 4A-D). The most evident significant relationship was with trophic similarity, i.e. the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C). Here it is noteworthy to highlight those high-trophic level species (TL > 3.1) with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Daption capense* and *Eudyptes chrysocome* (seabirds), Ziphiidae and *Lagenorhynchus cruciger* (marine mammals) (Table S3).

@@

We are indebted to all those experts of the working group 'Banco Burdwood' who humbly provided their knowledge to enhance the quality of the present research. It is worth to mention the following researchers: Brenda L. Doti (IBBEA, CONICET-UBA; Universidad de Buenos Aires, Argentina), Sofía L. Callá (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina), Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba, Argentina), Mariano I. Martinez (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina) and Luciano Padovani (Instituto Nacional de Investigación y Desarrollo Pesquero, INIDEP, Argentina).
Special thanks to G.A. Lovrich the Scientific Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA N-BB Administrators.
This study was funded by Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina. This work is contribution no. XX of the MPA Namuncurá (Law 26.875).

### 2023-05-08 MS_ToSubmit/MS_Burdwood_foodweb.tex
2nd version w/ coauthors suggs

We found different relationships between the species trophic level (TL)
and the rest of the analysed species-level properties (Figure 4A-D). The
most evident significant relationship was with trophic similarity,
i.e.~the higher the species' TL, the lower the trophic similarity or the
higher the uniqueness in terms of trophic role (Figure 4C). Here it is
noteworthy to highlight those high-trophic level species (TL
\textgreater{} 3.1) with low values of trophic similarity:
\emph{Bathyraja macloviana} and \emph{Squalus acanthias}
(Chondrichthyans), \emph{Diplopteraster clarki} and \emph{Pteraster sp}
(echinoderms), \emph{Phalacrocorax atriceps} and \emph{Eudyptes
chrysocome} (seabirds), and \emph{Lagenorhynchus cruciger} (marine
mammals) (Table S3).

@@

We are indebted to all those experts of the working group `Banco
Burdwood' who humbly provided their knowledge to enhance the quality of
the present research. It is worth to mention the following researchers:
Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba,
Argentina), Mariano I. Martinez (Museo Argentino de Ciencias Naturales
``Bernardino Rivadavia'', Argentina), Sofía L. Callá (Museo Argentino de
Ciencias Naturales ``Bernardino Rivadavia'', Argentina),\ldots{} Special
thanks to G.A. Lovrich the Scientific Coordinator of the MPA
Namuncurá-Burdwood Bank and the MPA N-BB Administrators. This study was
funded by Consejo Nacional de Investigaciones Científicas y Técnicas
(CONICET) and Agencia Nacional de Promoción Científica y Tecnológica
(PICT 2020-SERIEA-01617), Argentina. This work is contribution no. XX of
the MPA Namuncurá (Law 26.875).

>>>>

We found different relationships between the species trophic level (TL)
and the rest of the analysed species-level properties (Figure 4A-D). The
most evident significant relationship was with trophic similarity,
i.e.~the higher the species' TL, the lower the trophic similarity or the
higher the uniqueness in terms of trophic role (Figure 4C). Here it is
noteworthy to highlight those high-trophic level species (TL
\textgreater{} 3.1) with low values of trophic similarity:
\emph{Bathyraja macloviana} and \emph{Squalus acanthias}
(Chondrichthyans), \emph{Diplopteraster clarki} and \emph{Pteraster sp}
(echinoderms), \emph{Daption capense} and \emph{Eudyptes chrysocome}
(seabirds), Ziphiidae and \emph{Lagenorhynchus cruciger} (marine
mammals) (Table S3).

@@

We are indebted to all those experts of the working group `Banco
Burdwood' who humbly provided their knowledge to enhance the quality of
the present research. It is worth to mention the following researchers:
Brenda L. Doti (IBBEA, CONICET-UBA; Universidad de Buenos Aires,
Argentina), Sofía L. Callá (Museo Argentino de Ciencias Naturales
``Bernardino Rivadavia'', Argentina), Sandra Gordillo (IDACOR-CONICET;
Universidad Nacional de Córdoba, Argentina), Mariano I. Martinez (Museo
Argentino de Ciencias Naturales ``Bernardino Rivadavia'', Argentina) and
Luciano Padovani (Instituto Nacional de Investigación y Desarrollo
Pesquero, INIDEP, Argentina). Special thanks to G.A. Lovrich the
Scientific Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA
N-BB Administrators. This study was funded by Consejo Nacional de
Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de
Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina.
This work is contribution no. XX of the MPA Namuncurá (Law 26.875).
